Carbon Nucleosynthesis

### 2023-03-26 thesis/tex/main.tex
initial thesis commit

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{abbrevs}
% \usepackage{amssymb}	% Extra maths symbols
\graphicspath{{../figures/}}

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
\defcitealias{cristallo+11}{C11}
\defcitealias{cristallo+15}{C15}
\defcitealias{ventura+13}{V13}
\defcitealias{karakas10}{K10}
\defcitealias{KL16}{KL16}
\defcitealias{karakas+18}{K18}

@@

\newabbrev\CC{Core Collapse Supernovae (CCSNe)}[CCSNe]

@@

\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
\newcommand{\Ycc}{\ensuremath{Y_{\rm C}^{\rm cc}}}
\newcommand{\Yct}{\ensuremath{Y_{\rm C, 0}^{\rm tot}}}
\newcommand{\Yoc}{\ensuremath{Y_{\rm O}^{\rm cc}}}
\newcommand{\Ycagb}{\ensuremath{Y_{\rm C}^{\rm agb}}}

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Constraining carbon yields]{The galactic chemical evolution of carbon: Constraining stellar nucleosynthesis}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[D. A. Boyea et al.]{
Daniel A. Boyea,$^{1}$\
et al.
% James W. Johnson,$^{1}$
% David Weinberg
% Jack Roberts
% Jennifer Johnson
% ?
\\
% List of institutions
$^{1}$Department of Astronomy, The Ohio State University\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2023}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics. In this paper, we aim to estimate the nucleosynthetic yields of carbon using galactic chemical evolution models.

We find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times. 
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
Need to find some...
\end{keywords}

@@

\section{Introduction}

@@

Carbon and nitrogen are the only lighter elements produced significantly by low mass stars, so*****, reasons WHY this study.

@@

\CC are also important (.... SN reminant measurments)

@@

Previous models (CIte). We use \VICE (CITE) to create multi-zone models of GCE enabling us to account for the effects of migration on our predicted yields.

\citet{prantzos+18}
\citep{WAF17}
\citep{james+21}
\citep{fiorenzo+21}

\citep[e.g.][]{james+22}

One challenge of measuring abundances of carbon in star is that when a star becomes a RGB star, material from the CNO-processed core. Since this core-processed material is now carbon depleted and nitrogen enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.

@@

\begin{figure*}
    \centering
    \includegraphics[]{subgiants_mgh.pdf}
    \includegraphics[]{subgiants_mgfe.pdf}
    \caption{Chemical abundance relationships of our sample of APOGEE subgiants (see Jack et al. 2023). Left panel shows }
    \label{fig:subgiants}
\end{figure*}
\section{Nucleosynthesis}

@@

\subsection{Asymptotic giant branch carbon}

@@

An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during the final phases of evolution. The star has already completed hydrogen core burning, Hydrogen shell burning during the red giant branch phase, and helium core burning. So, the structure consists of an inert core of carbon and oxygen surrounded by a helium burning shell and a hydrogen burning shell. The double shell burning leads to thermal instabilities which drive off the outer layers of the star in a series of violent pulsations, ejecting the envelope and leaving behind a C/O white dwarf.

In an AGB star, two competing processes determine the outcome of carbon production.
Third Dredge Up (TDU) is needed to eject carbon from the star, enriching the surface with helium-burning-processed material from the core. But Hot Bottom Burning (HBB) at the base of the convection layer changes carbon into nitrogen. 
TDU occurs during thermal pulsations, where the convective layer of the star passes into the inner layers with He-burning products which mixes in C and O into the envelope. In contrast, HBB may happen if the base of the convective envelope reaches about 50MK, initiating the CNO cycle, converting most C12 into N14.

@@

\subsection{CCSNe carbon}

\begin{figure*}
    \includegraphics[scale=0.9]{y_c_cc-2.pdf}
    \includegraphics[scale=0.9]{y_co_cc.pdf}
    \caption{The fist plot shows IMF-weighted net fractional CCSNe yield of
        carbon, $y_C^{cc}$ against metalicity, [M/H], for different studies.
        The right plot instead shows [C/O]$^\text{CC}$, the logarithm of the
        abundance ratio of carbon to oxygen if CCSNe were the only carbon
        source, also as a function of metallicity for the same set of studies.
        The black line represents the carbon yield of the fiducial model,
        $y_C^{CC} = 0.004? (Z/Z_{\sun})^{0.3}$, and becomes dashed over regions
        where we have not tested our model.\citep{NKT13}, \citep{LC18},
        \citep{sukhbold+16}, \citep{WW95}
 }
    \label{fig:y_cc}
\end{figure*}

@@

    \section{The Multizone Model}\label{sec:vice}

@@

\subsection{Model Stellar Yields}
We define a parameterization of a \CC~yield
  Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks. We find that a powerlaw yield with a metallicity-dependent constant minimum is able to match the observations well while remaining a simple parameterization (see below). Our expression is:
  \begin{equation}\label{eq:y_yields}
   Y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta Y_\text{O}^\text{CC} + Y_\text{C, 0}^\text{CC}
    \end{equation}
   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{sec:equilibrium} ). Our second model uses $\alpha = 0.44$ and $\beta = 0.63$ with K16 yields and reduced $\eta \rightarrow 1/2 \eta$

@@

\section{Multizone model results}

\subsection{Data Selection}

@@

\subsection{The Evolution of carbon across the galaxy and through time}

\begin{figure*}
\label{fig:c_evo}
\includegraphics{evo_tracks-9.pdf}
\includegraphics{evo_slices-2.pdf}
\caption{The top set of panes show the time evolution of the gas phase of our
    fiducial model, plotted as tracks through \caah and \caafe where each colored line corresponds to the evolution at that galactic radius. 
The bottom set instead shows the galaxies gas-phase \caah and \caafe trend at 5 different time slices. 
}
\end{figure*}

@@

\subsection{Effects of AGB Yields}

\begin{figure*}
\includegraphics[scale=0.6]{oob_agb-1.pdf}

@@

As we chose to leave $Y_{\rm C}^{\rm CC}$ in a functional form, we chose to
leave the total IMF-averaged carbon yield to be constant. The magnitude of
$Y_{\rm C}^{\rm CC}$
\begin{equation}
    Y_{\rm C}^{0}  = 0.005  =  Y_{\rm C}^{\rm cc} + Y_{\rm C}^{\rm agb}
\Big \rvert_{Z=Z_\odot}
\end{equation}
where we are choosing to evaluate the total IMF \CC and AGB yields at solar
metallicity. We show our calculations of $Y_{\rm C}^{\rm agb}(Z=Z_{\sun })$  in
Table \ref{tab:alpha_agb}.

@@

As the highest AGB yield at solar is from our \karakas~model at $Y_{\rm C}^{\rm
agb} = 0.000585$ is only 11.7 percent of our required total carbon production,
each of these models is dominated by \CC production of carbon. As a result,
while the metallicity dependence of the \caah may vary, the
\caafe diagnostic shows how this small AGB fraction makes the details of
the AGB model and delay-time-distribution unchange the galaxy production of
carbon.

@@

\subsection{Metallicity dependence and the AGB Fraction}

\begin{figure*}\label{fig:beta_f}
\includegraphics[scale=0.6]{beta-1.pdf}
\includegraphics[scale=0.6]{f_agb-1.pdf}

@@

\subsection{The AGB Fraction }
One potential tension with data is our models predict a low value for the AGB fraction of stars.

@@

\subsection{Star Formation History}

\begin{figure*}
\includegraphics[scale=0.6]{lateburst_eta-1.pdf}

@@

\subsection{Outflows}
A common degeneracy in chemical evolution models is the yield-outflow degeneracy. An increase in stellar yields has a near-identical effect as a decrease in outflows. However, reducing the outflows reduces the evolution timescale of the system.

@@

\subsection{Understanding Scatter}

\begin{figure}
    \includegraphics[scale=0.6]{cooh_scatter.pdf}
    \caption{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{cnoh.pdf}
    \caption{Caption}
    \label{fig:cnofe}
\end{figure}

@@

\subsection{Comparison to Observations}

@@

\section{The Equilibrium Approximation}\label{sec:equilibrium}
If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio. Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.  
We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
\begin{equation}
M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
\end{equation}

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.3]{analytic_y-4.pdf}
    \caption{Our reverse fitting method to determine total CCSNe contribution}
\end{figure}

@@

\subsection{Uncertainties}

@@

\section{Conclusions}

@@

\section*{Acknowledgements}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data Availability}

@@

\bibliographystyle{mnras}
\bibliography{main} % if your bibtex file is called example.bib

@@

\section{Validating the APOGEE Subgiant Sample}\label{sec:jack}
Our APOGEE subgiant sample excludes stars marked with the following flags:
\begin{itemize}
\item \texttt{ancillary young embedded cluster}
\item \texttt{ancillary emission line star}
\item \texttt{MIR-deected candidate cluster member}
\item \texttt{selected as part of the EB program}
\item \texttt{selected as part of the young cluster study (in-SYNC)}
\item \texttt{W3/4/5 star forming complex}
\end{itemize}

@@

In the first panel, both V13 and the subgiant sample predict similar trends in [C/Mg]-[Mg/H] but there appears to be a systematic offset of about 0.2dex. Reproducing the trend is promising as V21's mixing corrections were metallicity-dependent so the uncorrected sample of APOGEE giants does not match the subgiant trend.

The systematic offset could be explained by overpredicting the effects of FDU or other *** in V21's stellar evolution models??? or other subgiant physics???

In the second panel, agreement appears to be better. Both the MDF and the slope are nearly identical,
There is a slight deviation in slope between the models, and this could again be a systematic such as underestimation of **8some stellar effect**** at higher metallicities.

We compare both of **** in Fig. \ref{fig:fiorenzo_jack}.

\begin{figure*}
    \centering
    \includegraphics[scale=0.5]{fiorenzo_vs_jack_c-1.pdf}
    \includegraphics[scale=0.5]{fiorenzo_vs_jack_n-1.pdf}
    \caption{A comparison of estimated stellar birth abundance trends from the subgiant sample and
        \citet{fiorenzo+21}
    }
    \label{fig:fiorenzo_jack}
\end{figure*}

\section{Effects of Alternate AGB Models}\label{sec:alt_agb}

@@

\begin{figure*}
\includegraphics[scale=0.45]{agb_adj-2.pdf}
\includegraphics[scale=0.45]{abg_adj_z-1.pdf}

@@

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

>>>>

\documentclass[12pt,oneside]{book}

% \AddToHook{cmd/section/before}{\clearpage}

\usepackage[T1]{fontenc}

\usepackage{aas_macros}
\usepackage[letterpaper, top=1in]{geometry}
\usepackage{titlesec}

\titleformat{\chapter}{\normalfont\normalsize\centering}{Chapter \thechapter:}{1em}{}
\titleformat{\section}{\normalfont\normalsize\centering}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\normalsize\centering}{\thesubsection}{1em}{}
\titlespacing*{\chapter}{0pt}{-15pt}{40pt} \titlespacing*{\section}{0pt}{0pt}{20pt}
\renewcommand{\contentsname}{Table of Contents}

\usepackage{setspace}

\usepackage{amsmath}	% Advanced maths commands
\usepackage{txfonts}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    pdftitle={Thesis},
    pdfpagemode=FullScreen,
}
% \usepackage{amssymb}	% Extra maths symbols

\usepackage{graphicx}	% Including figure files
\graphicspath{{../figures/}}

\usepackage{natbib}
\usepackage[nottoc,numbib]{tocbibind}

% \usepackage{fancyhdr}
% \pagestyle{fancy}
% \fancyhead{}
% \fancyhead[RO,RE]{Carbon Galactic Nucleosynthesis}
\pagestyle{plain}

\defcitealias{cristallo+11}{C11}
\defcitealias{cristallo+15}{C15}
\defcitealias{ventura+13}{V13}
\defcitealias{karakas10}{K10}
\defcitealias{KL16}{KL16}
\defcitealias{karakas+18}{K18}

@@

@@

\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm cc}}}
\newcommand{\Yct}{\ensuremath{y_{\rm C, 0}^{\rm tot}}}
\newcommand{\Yoc}{\ensuremath{y_{\rm O}^{\rm cc}}}
\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm agb}}}
\newcommand{\sun}{\ensuremath{\odot}}

\title{Carbon Nucleosynthesis}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author{Daniel A. Boyea}

% These dates will be filled out by the publisher
\date{\today}

\pagenumbering{roman}

\begin{document}

%\doublespacing

\begin{titlepage}
   \begin{center}
       \vfill
       \textbf{The Galactic Chemical Evolution of Carbon} \\
        Implications for nucleosynthesis
        \vfill
        Research Thesis
        \vfill
        Presented in partial fulfillment of the requirements for graduation \textit{with research distinction} in Astronomy and Astrophysics in the College of Arts and Sciences of The Ohio State University.
        \vfill
        by 
        \vfill
       {Daniel A. Boyea}\\
       \vfill
       Department of Astronomy\\
       The Ohio State University\\
       \vfill
       April 2023
       \vfill
       Thesis Committee:\\
       David Weinberg, Advisor \\
       Jennifer Johnson \\
       Rolando Vald\'es Aguilar\\
       \vfill

   \end{center}
\end{titlepage}

% Abstract of the paper
\chapter*{Abstract}
\begin{center}
Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics. In this paper, we aim to estimate the nucleosynthetic yields of carbon using galactic chemical evolution models.

We find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times. 
\end{center}

\chapter*{Acknowledgements}

Many thanks to

%% Lists

\tableofcontents
\listoffigures
\listoftables
\newpage
\pagenumbering{arabic}

@@

\chapter{Introduction}

@@

Carbon and nitrogen are well studied elements as they are easy to observe (Citations...). Additionally, carbon and nitrogen are used as age indicators for giant branch stars (citations, e.g. \cite{fiorenzo+21}), and are the only light elements known to be produced significantly in Asymptotic Giant Branch Stars (AGB) (cite).

However, theoretical interpretations of the trends of

While easily visible in many stars, determining birth abundances of carbon and nitrogen are

One challenge of measuring abundances of carbon in star is that when a star becomes a RGB star, material from the CNO-processed core. Since this core-processed material is now carbon depleted and nitrogen enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.
Additionaly, carbon is extremelt challenging to measure gas-phase abundances for because the strongest visible line is ...., e.g. carbon unreliable in GALAH, low detections.

@@

CCSne are also important (.... SN reminant measurments)

@@

@@

\begin{figure}[htp]
    \centering
    \includegraphics[scale=0.85]{subgiants_mgh.pdf}
    \includegraphics[scale=0.85]{subgiants_mgfe.pdf}
    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (left) and [Mg/Fe] (right). The left panel uses blue and orange to represent high and low $\alpha$ sequences respectively. On the right, we plot more metal rich ([Mh/H]) stars with darker colors.}
    \label{fig:subgiants}
\end{figure}
\chapter{Nucleosynthesis}

@@

\section{Asymptotic giant branch carbon}

@@

An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during the final phases of evolution.  In an AGB star, two competing processes determine the outcome of carbon production.
Third Dredge Up (TDU) is needed to eject carbon from the star, enriching the surface with helium-burning-processed material from the core. But Hot Bottom Burning (HBB) at the base of the convection layer changes carbon into nitrogen. 
TDU occurs during thermal pulsations, where the convective layer of the star passes into the inner layers with He-burning products which mixes in C and O into the envelope. In contrast, HBB may happen if the base of the convective envelope reaches about 50MK, initiating the CNO cycle, converting most C12 into N14.

@@

\section{CCSNe carbon}

\begin{figure}[htp]
    \includegraphics[scale=0.8]{y_c_cc-2.pdf}
    \includegraphics[scale=0.8]{y_co_cc.pdf}
    \caption{The fist plot shows IMF-weighted net fractional CCSNe yield of
        carbon, $y_C^{cc}$ against metalicity, [M/H], for different studies.
        The right plot instead shows [C/O]$^\text{CC}$, the logarithm of the
        abundance ratio of carbon to oxygen if CCSNe were the only carbon
        source, also as a function of metallicity for the same set of studies.
        The black line represents the carbon yield of the fiducial model,
        $y_C^{CC} = 0.004? (Z/Z_{\sun})^{0.3}$, and becomes dashed over regions
        where we have not tested our model.\citep{NKT13}, \citep{LC18},
        \citep{sukhbold+16}, \citep{WW95}
 }
    \label{fig:y_cc}
\end{figure}

@@

\chapter{The Multizone Model}\label{sec:vice}

@@

\section{Model Stellar Yields}
We define a parameterization of a CC~yield
  Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks. We find that a powerlaw yield with a metallicity-dependent constant minimum is able to match the observations well while remaining a simple parameterization (see below). Our expression is:
  \begin{equation}\label{eq:y_yields}
   Y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta Y_\text{O}^\text{CC} + Y_\text{C, 0}^\text{CC}
    \end{equation}
   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{sec:equilibrium} ). Our second model uses $\alpha = 0.44$ and $\beta = 0.63$ with K16 yields and reduced $\eta \rightarrow 1/2 \eta$

@@

\chapter{Multizone model results}
\section{Data Selection}

@@

\section{The Evolution of carbon across the galaxy and through time}

\begin{figure*}
\label{fig:c_evo}
\includegraphics{evo_tracks.pdf}
\includegraphics{evo_slices.pdf}
\caption{The top set of panes show the time evolution of the gas phase of our
    fiducial model, plotted as tracks through \caah and \caafe where each colored line corresponds to the evolution at that galactic radius. 
The bottom set instead shows the galaxies gas-phase \caah and \caafe trend at 5 different time slices. 
}
\end{figure*}

@@

\section{Effects of AGB Yields}

\begin{figure*}
\includegraphics[scale=0.9]{oob_agb.pdf}

@@

As we chose to leave $Y_{\rm C}^{\rm CC}$ in a functional form, we chose to
leave the total IMF-averaged carbon yield to be constant. The magnitude of
$Y_{\rm C}^{\rm CC}$
\begin{equation}
    Y_{\rm C}^{0}  = 0.005  =  Y_{\rm C}^{\rm cc} + Y_{\rm C}^{\rm agb}
\Big \rvert_{Z=Z_\odot}
\end{equation}
where we are choosing to evaluate the total IMF CC and AGB yields at solar
metallicity. We show our calculations of $Y_{\rm C}^{\rm agb}(Z=Z_{\sun })$  in
Table \ref{tab:alpha_agb}.

@@

As the highest AGB yield at solar is from our \karakas~model at $Y_{\rm C}^{\rm
agb} = 0.000585$ is only 11.7 percent of our required total carbon production,
each of these models is dominated by CC production of carbon. As a result,
while the metallicity dependence of the \caah may vary, the
\caafe diagnostic shows how this small AGB fraction makes the details of
the AGB model and delay-time-distribution unchange the galaxy production of
carbon.

@@

\section{Metallicity dependence and the AGB Fraction}

\begin{figure*}\label{fig:beta_f}
\includegraphics{beta.pdf}
\includegraphics{f_agb.pdf}

@@

One caveat is that the slope of this trend is also determined by the ratio of delayed iron to CCSNe iron production as well. If the SNeIa iron fraction is increased, then more iron enters later reducing the slope of the trend as AGB becomes a more rapid mechanism than Fe comparatively. The difference however is that changing the Fe franction mostly affects the tail of the distribution as this controls the speed of descent off the high $\alpha$ sequence, but the AGB fraction even changes the behavior for the low $\alpha$ sequence.

\section{The AGB Fraction }
One potential tension with data is our models predict a low value for the AGB fraction of stars.

@@

\section{Star Formation History}

\begin{figure*}
\includegraphics[]{lateburst_eta.pdf}

@@

\section{Outflows}
A common degeneracy in chemical evolution models is the yield-outflow degeneracy. An increase in stellar yields has a near-identical effect as a decrease in outflows. However, reducing the outflows reduces the evolution timescale of the system.

@@

\section{Understanding Scatter}

\begin{figure*}
    \includegraphics[scale=0.9]{cooh_scatter.pdf}
    \includegraphics[scale=0.9]{cnoh_scatter.pdf}
    \caption{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
\end{figure*}

@@

\section{Comparison to Observations}

@@

\chapter{The Equilibrium Approximation}\label{sec:equilibrium}
If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio. Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.  
We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
\begin{equation}
M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
\end{equation}

@@

\begin{figure}
    \centering
    \includegraphics[]{analytic.pdf}
    \caption{Our reverse fitting method to determine total CCSNe contribution}
\end{figure}

@@

\section{Uncertainties}

@@

\chapter{Conclusions}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Data Availability}

@@

\bibliographystyle{aasjournal}
\bibliography{main} % if your bibtex file is called example.bib

@@

\chapter{Validating the APOGEE Subgiant Sample}\label{sec:jack}
Our APOGEE subgiant sample excludes stars marked with the following flags:
\begin{itemize}
\item \texttt{ancillary young embedded cluster}
\item \texttt{ancillary emission line star}
\item \texttt{MIR-deected candidate cluster member}
\item \texttt{selected as part of the EB program}
\item \texttt{selected as part of the young cluster study (in-SYNC)}
\item \texttt{W3/4/5 star forming complex}
\end{itemize}

@@

\chapter{Effects of Alternate AGB Models}\label{sec:alt_agb}

@@

\begin{figure*}
    \includegraphics{coofe_agb_extra.pdf}
    \includegraphics{coofe_agb_extra_0.2.pdf}

@@

\label{lastpage}
\end{document}
